\textbf{Generalized additive models to analyze biomedical non-linear longitudinal data in R: Beyond repeated measures ANOVA and Linear Mixed Models}

### 2021-12-28 Manuscripts/Manuscript_by_chapters-SIM_Revisions_final/sections/04-Longitudinal analysis with GAMs.Rmd
Fixed error on gratia::vcov

#the same model used for the full dataset
mod_m1 <- gam(StO2_sim ~ Group+s(Day,by=Group,k=5), data  = dat_missing)
#appraise the model
appraise(mod_m1)

>>>>

#the same model used for the full dataset
mod_m1 <- gam(StO2_sim ~ Group+s(Day,by=Group,k=5),
              method='REML',
              data  = dat_missing)
#appraise the model
appraise(mod_m1)
